\begin{thebibliography}{99}
\setlength{\parskip}{1em}

\bibitem{Snijders}
Snijders, C.; Matzat, U.; Reips, U.-D. (2012). "Big Data: Big gaps of knowledge in the field of Internet." International Journal of Internet Science. 7: 1–5.

\bibitem{Brown}
Brown, J. M.  and L. D. Attardi, “The role of apoptosis in cancer development and treatment response,” Nat. Rev. Cancer 5(3), 231-237 (2005).

\bibitem{Foley}
Foley, J. D.; and A. Fan Dam. (1982). Fundamentals of Interactive Computer Graphics. Reading, MA: Addison-Wesley. ISBN 0201144689.

\bibitem{Linda}
Shapiro, Linda G.  and George C. Stockman, Computer Vision. Upper Saddle River: Prentice–Hall, 2001

\bibitem{Nanni}
Nanni L., et al. , “Different approaches for extracting information from the co-occurrence matrix,” PLoS One 8(12), e83554 (2013).

\bibitem{Mitchell}
Mitchell, T. (1997). Machine Learning, McGraw Hill. ISBN 0-07-042807-7, p.2.

\bibitem{Mehryar}
Mehryar Mohri, Afshin Rostamizadeh, Ameet Talwalkar (2012) Foundations of Machine Learning, The MIT Press ISBN 9780262018258.

\bibitem{Cortes}
Cortes, C.; Vapnik, V. (1995). "Support-vector networks". Machine Learning. 20 (3): 273–297. doi:10.1007/BF00994018.

\bibitem{Aizerman}
Aizerman, M. A.; Braverman, Emmanuel M.; Rozoner, L. I. (1964). "Theoretical foundations of the potential function method in pattern recognition learning". Automation and Remote Control. 25: 821–837. Cited in Guyon, Isabelle; Boser, B.; Vapnik, Vladimir (1993). Automatic capacity tuning of very large VC-dimension classifiers. Advances in neural information processing systems. CiteSeerX 10.1.1.17.7215Freely accessible.

\bibitem{Haralick}
R. M. Haralick, K. Shanmugam, and I. Dinstein, "Textural features for image classification," IEEE Trans. on Systems, Man, and Cybernetics, SMC-3, 610-621 (1973).

\bibitem{Gomez}
W. Gomez, W.C.A. Pereira, and A.F.C Infantosi, "Analysis of cooccurance texture statistics as a function of gray-level quantization for classifying breast ultrasound," Trans. Medical Imaging, vol. 31, no. 10, pp. 1889-1899, 2012.

\bibitem{Umasankar}
Umasankar Kandaswamy, A. Adjeroh Donald, M. C. Lee, "Efficient Texture Analysis of SAR Imagery", IEEE Transaction on Geoscience and Remote Sending, vol. 43, no. 9, pp. 2075-2083, 2005.

\bibitem{Biswajit}
Biswajit Pathak, Debajyoti Barooah. "TEXTURE ANALYSIS BASED ON THE GRAY-LEVEL CO-OCCURRENCE MATRIX CONSIDERING POSSIBLE ORIENTATIONS." International Journal of Advanced Research in Electrical, Electronics and Instrumentation Engineering 

\bibitem{Peng}
Gong, Peng, Danielle J. Marceau, and Philip J. Howarth. "A comparison of spatial feature extraction algorithms for land-use classification with SPOT HRV data." Remote sensing of environment 40.2 (1992): 137-151.

\bibitem{Albregtsen}
Fritz Albregtsen. "Statistical Texture Measures Computed from Gray Level Coocurrence Matrices." Image Processing Laboratory, Department of Informatics, University of Oslo. (November 5, 2008).

\bibitem{Thati}
Sai Kiran Thati, Junhua Ding, Dongmei Zhang, Xin Hua Hu. "Feature Selection and Analysis of Diffraction Images." Software Quality, Reliability and Security - Companion (QRS-C), 2015 IEEE International Conference on.

\bibitem{Jiantao}
Software Testing by Jiantao Pan, Carnegie Mellon University

\bibitem{Kaner}
Kaner, Cem; A Course in Black Box Software Testing, 2004

\bibitem{Feng}
Y. Feng et al., “Polarization imaging and classification of Jurkat T and Ramos B cells using a flow cytometer,” Cytometry A 85(9), 817–826(2014).

\bibitem{Zhang}
J. Zhang et al., “Analysis of cellular objects through diffraction images acquired by flow cytometry,” Opt. Express 21(21), 24819–24828(2013).

\bibitem{McCulloch}
McCulloch, Warren; Walter Pitts (1943). "A Logical Calculus of Ideas Immanent in Nervous Activity". Bulletin of Mathematical Biophysics. 5 (4): 115–133. doi:10.1007/BF02478259.

\bibitem{Chang}
C.-C. Chang and C.-J. Lin. LIBSVM: a library for support vector machines. ACM
Transactions on Intelligent Systems and Technology, 2(3):27:1–27:27, 2011. Software
available at http://www.csie.ntu.edu.tw/~cjlin/libsvm

\bibitem{Rakesh}
Rakesh Asery, Ramesh Kumar Sunkaria, Lakhan Dev Sharma, Aman Kumar. "Fog detection using GLCM based features and SVM." Advances in Signal Processing (CASP), Conference on.

\bibitem{Qayyum}
R. Qayyum, K. Kamal, T. Zafar, S. Mathavan. "Wood defects classification using GLCM based features and PSO trained neural network." Automation and Computing (ICAC), 2016 22nd International Conference on.
\end{thebibliography}
